Estimating duration in the presence of misclassification

### 2024-03-25 introduction.tex
plural data

An example of incidence-type data is community testing.
This relies on individuals presenting for a test, hence is biased by individuals' ability and willingness to be tested.

@@

In order to best fulfil this thesis's primary aim, the methodology developed should be easy for others to use.
Therefore, the code for the analyses in this thesis is available online.
An index to the code and, where possible, data is available at \url{https://github.com/joshuablake/thesis-index}.
I structured two elements of the code as R packages to enable their application to future contexts.

>>>>

An example of incidence-type data are community testing.
This relies on individuals presenting for a test, hence is biased by individuals' ability and willingness to be tested.

@@

In order to best fulfil this thesis's primary aim, the methodology developed should be easy for others to use.
Therefore, the code for the analyses in this thesis is available online.
An index to the code and, where possible, data are available at \url{https://github.com/joshuablake/thesis-index}.
I structured two elements of the code as R packages to enable their application to future contexts.
